sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-12-06 inst/documents/sensi_an_rotations1.Rmd
comments

    ## variable inputs ##
    linputs$cost <-           runif(1, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(1, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(1, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(1, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(1, min=0,   max=1)
    linputs$dom_cos <-        runif(1, min=0,   max=1) 
    linputs$start_freqs <-    runif(1, min=0.005,   max=0.1) #note not log yet   
    linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1
    # dispersal (initially with cost set to 0)
    #linputs$coverage <-       runif(1, min=0.1, max=0.9)
    #linputs$migration <-      runif(1, min=0.1, max=0.9)

@@

>>>>

    ## variable inputs ##
    linputs$cost <-           runif(1, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(1, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(1, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(1, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(1, min=0,   max=1)
    linputs$dom_cos <-        runif(1, min=0,   max=1) 
    #TODO make this lognormal to get lower frequencies too
    linputs$start_freqs <-    runif(1, min=0.005,   max=0.1) #note not log yet   
    linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1
    # dispersal (initially with cost set to 0)
    #linputs$coverage <-       runif(1, min=0.1, max=0.9)
    #linputs$migration <-      runif(1, min=0.1, max=0.9)

@@

    # previously I used rbind this scenario inputs & results onto previous
    # not a good speed or memory way of doing
    #df_res_all <- rbind(df_res_all, df_in_out)

    # now replaced with this better way
    # set a dataframe for the outputs to the required size in scenario1
    if (i==1)
    {
      df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=n_scenarios))
      names(df_res_all) <- names(df_in_out)
    }
